\documentclass[mres]{ucl_thesis}
%twoside for double page printing
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{epsfig}
\usepackage{subfigure}
%\renewcommand{\familydefault}{\sfdefault}
%\usepackage{palatino}
%\usepackage{lmodern}
%\fontsize{20}{24}\selectfont



\title{Using Congestion Exposure for Traffic Engineering (May be misleading)}
\author{Imad GRANDI}

%\renewcommand{\baselinestretch}{1.5}
%\renewcommand{\bibname}{References}

\bibliographystyle{alpha}

\begin{document}
\maketitle

\clearpage
\clearpage
\fontsize{12}{15}
\selectfont
\begin{center}
\textbf{To whomever}
\end{center}

\include{src/intro/abstract}
\include{src/intro/ack}

\setcounter{tocdepth}{2}
\tableofcontents
\listoffigures
\listoftables

\cleardoublepage

\include{src/intro/intro}

\include{src/state/intro}
\include{src/state/te}
\include{src/state/cc}
\include{src/state/conex}

\include{src/preflex/intro}
\include{src/preflex/preflex}

\include{src/implementation/intro}
\include{src/implementation/implementation}

\include{src/results/intro}
\include{src/results/results}

\include{src/conclusion/intro}
\include{src/conclusion/conclusion}

\addcontentsline{toc}{chapter}{section}{Appendices}

\chapter{Appendices}
%\appendix
%\input{appendix}

\addcontentsline{toc}{chapter}{Bibliography}

\bibliography{PhD}
\begin{thebibliography}{9}
\bibitem[RFC 3272]{RFC3272}D. Awduche, A. Chiu, A. Elwalid, I. Widjaja, X. Xiao. \emph{Overview and Principles of Internet Traffic Engineering}. RFC 3272, IETF, May 2002. (pp 4, 14, )
\bibitem[Awduche02]{awd1}D. Awduche, A. Chiu, A. Elwalid, I. Widjaja, X. Xiao. \emph{Overview and Principles of Internet Traffic Engineering}. May 2002.

\bibitem[Kandula05]{kan1}S. Kandula, D. Katabi, B .Davie, A. Charny. \emph{Walking the Tightrope: Responsive Yet Stable Traffic Engineering}. August 2005. 

\bibitem[Gojmerac03]{goj1}I. Gojmerac, T. Ziegler, F. Ricciato, P. Reichl. \emph{Adaptive Multipath Routing for Dynamic Traffic Engineering}. 2003.
\bibitem[Toguyni09]{tog09}A. Toguyni, O. Korbaa. \emph{DiffServ Aware MPLS Traffic
Engineering for ISP Networks: State of the Art and New Trends}. January 2009.
\bibitem[Sinha04]{sin1}S. Sinha, S. Kandula, D. Katabi. \emph{Harnessing TCPs Burstiness with Flowlet Switching}. 2004. 
\bibitem[Elwalid01]{elwal1}A. Elwalid, C. Jin, S. Low, I. Widjaja. \emph{MATE: MPLS Adaptive Traffic Engineering}. IETF, 2001. 
\bibitem[Xiao00]{xia1}X Xiao, A. Hannan, B. Bailey, L. M. Ni. \emph{Traffic Engineering with MPLS in the Internet}. IETF, 2000. 
\bibitem[Raiciu09]{rai1}C. Raiciu, D. Wischik, M. Handley. \emph{Practical Congestion Control for Multipath Transport Protocols}. 2009.
\bibitem[Bennett99]{ben1}J. C. R. Bennett, C. Partridge, N. Shectman. \emph{Packet Reordering is Not Pathological Network Behavior}. DECEMBER 1999. 
\bibitem[Araujo09]{arau1}J.Araujo, M. Rio, G. Pavlou. \emph{A Mutualistic Resource Pooling Architecture}.   2010. 
\bibitem[Fortz00]{fortz00}B. Fortz and M. Thorup. \emph{Internet Traffic Engineeringby Optimizing OSPF Weights.} In Proceedings of IEEE Infocom 2000, Tel Aviv, Israel, March 2000. (pp 32, 69)
\bibitem[Jacobson88]{jaco88}V. Jacobson and M. Karels. \emph{Congestion Avoidance and Control. Computer Communication Review,} Proceedings of ACM SIGCOMM 1988.


\end{thebibliography}

\end{document} 
