\documentclass[mres, **20pt**]{ucl_thesis}
%twoside for double page printing
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{setspace}
%\renewcommand{\familydefault}{\sfdefault}
%\usepackage{palatino}
%\usepackage{lmodern}
%\fontsize{20}{24}\selectfont



\title{Using Congestion Exposure for Traffic Engineering (May be misleading)}
\author{Imad GRANDI}

%\renewcommand{\baselinestretch}{1.5}
%\renewcommand{\bibname}{References}

\bibliographystyle{alpha}

\begin{document}
\maketitle

\clearpage
\clearpage
\fontsize{12}{15}
\selectfont
\begin{center}
\textbf{To whomever}
\end{center}

\begin{abstract}
If I knew my thesis, I would know my abstract and guess what? It
would be HERE.
\end{abstract}

\begin{acknowledgements}
Words comprising the acknowledgements.
\end{acknowledgements}

\setcounter{tocdepth}{2}
\tableofcontents
\listoffigures
\listoftables

%\cleardoublepage

\chapter{Introduction}
This is adraft that resumes the ideas that i want to speak about in the introduction

Internet is growing and also expectaion bla bla . One of  engineering solution is path diversity, has multiple advantages robustesness bla bla, but the network is not efficielty benefitting from the path diversity, and the problem is in the internet design itself. The small problem, is that pooling has being always seen as a network thing, rising from transport guys says that they could do better since they have an end-to-end visbility. Actually they are right about the last point. This is one of the problems with the Internet design. The hourglass concept implies that the network should be kept dumb and all the intelligence should be kept at the edge. The reason behing this dogmm are diminishing, the equipement caapcity is increasing exponentially and the network providers are alreasy breaching it for diverse reasons. This problem exist also in congestion control. Network lack  information to identify the responsibles for the congestions and are not doing that good in tehir attempts for dividing the capacity among their customers. Congestion exposure is one of the solutions, that allow to reveal to the network the congestion that a host is experiencing and though his participation for it.

But, this information could be also used for exploring path diversity. PREFLEX, is an architecture that uses this concepts and try to use it for balancing the traffic. The aim of this project was to evaluate how balancing could be done using this new architecture and then compare its performance with a tradditional traffic engineering approach for path diversity which is TEXCP that uses load instead of congestion.

%\fontencoding{\encodingdefault}
%\fontfamily{\familydefault}
%\fontseries{\seriesdefault}
%\fontshape{\shapedefault}
%\onehalfspacing

\label{intro}
\section{Overview}     % section 1.1
\section{Objectives}
\section{Document Structure}

\chapter{Background and state-of-the-art}
\input{TE}
\input{CC}
\input{ConEx}
%\section{Resource Pooling}
%\section{Traffic Splitting ?????}
%\subsection{Granularity: packet, flowlet, flow ...}
\chapter{PREFLEX }
\input{PREFLEX}
\chapter{Implementation}
\input{Impl}
\chapter{Simulation Results and Analysis}
\section{Analysis of PREF as a splitting mechanism}
\section{Load balancing VS congestion balancing}
\section{Analysis of PREFLEX balancing algorithm}
\section{Using traffic shapers for controlling the congestion}
\chapter{Conclusions and future work}
\section{conclusion}
\section{summary of contributions}
\section{Future Work}
%\label{conclusion}
%\input{conclusion}

\addcontentsline{toc}{chapter}{section}{Appendices}

\chapter{Appendices}
%\appendix
%\input{appendix}

\addcontentsline{toc}{chapter}{Bibliography}

\bibliography{PhD}
\begin{thebibliography}{9}
\bibitem[RFC 3272]{RFC3272}D. Awduche, A. Chiu, A. Elwalid, I. Widjaja, X. Xiao. \emph{Overview and Principles of Internet Traffic Engineering}. RFC 3272, IETF, May 2002. (pp 4, 14, )
\end{thebibliography}

\end{document} 